Pages written in 2022

### 2023-01-07 text/22/2022.Rmd
Added date checks to 2022.Rmd

```{r setup, echo=FALSE}
library(glue)
library(magrittr)
library(stringr)
yr <- 2023:1999
glue("[{yr}](http://new.pmean.com/{yr}/)") %>%
  paste(collapse=" | ") -> yr_list
list.files() %>%
  str_subset("md$") %>%
  str_replace(fixed(".Rmd"), "") %>%
  str_replace(fixed(".md"), "") -> f
n <- length(f):1
header <- glue("New website ({n[1]} files)")
glue("+ [{f}](http://new.pmean.com/{f}/)  ") %>%
  paste(collapse="  \n") -> file_list
```

@@

>>>>

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
library(glue)
library(magrittr)
library(readr)
library(stringr)
yr <- 2023:1999
glue("[{yr}](http://new.pmean.com/{yr}/)") %>%
  paste(collapse=" | ") -> yr_list
list.files() %>%
  str_subset("md$") -> f
```

```{r}
problem_files <- NULL
for (fn in f) {
  file_text <- read_lines(fn)
  file_text %>%
    str_subset("^source\\: ") %>%
    str_remove(fixed("source: ")) %>%
    str_remove_all(fixed('"')) %>%
    tolower -> file_source
  if (length(file_source)>1) {
    problem_files %<>% append(glue("{fn} has multiple sources\n"))
  }
  if (length(file_source)>0 & file_source[1]!="new") {
    problem_files %<>% append(glue("{fn} has source={file_source}\n"))
  }
  file_text %>%
    str_subset(fixed("date: ")) %>%
    str_remove(fixed("date: ")) -> file_date
  if (length(file_date)==0) {
    problem_files %<>% append(glue("{fn} has no date"))
  }
}
```

```{r}
f %>%
  str_replace(fixed(".Rmd"), "") %>%
  str_replace(fixed(".md"), "") -> f
n <- length(f):1
header <- glue("New website ({n[1]} files)")
glue("+ [{f}](http://new.pmean.com/{f}/)  ") %>%
  paste(collapse="  \n") -> file_list
```

@@

```{r}
if (length(problem_files)==0) {
  problem_files <- "All files passed date and source quality checks"
}
print(problem_files)
```
